Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-04-06 manuscript/manuscript.tex
minor ms changes

@@

@@

>>>>

New mutations are the ultimate source of all adaptations, but the vast majority
of mutations are neutral or decrease fitness. Negative selection acts to remove
these deleterious mutations with varying degrees of effectiveness, depending on
the magnitudes of two stochastic evolutionary processes: drift and draft.
Increasing the rate of either drift or draft inflates the variance in allele
frequency changes between generations, which decreases the efficiency of
negative selection. When population sizes are small or genomes are very tightly
linked, deleterious mutations can persist longer, or even fix in the
population. Numerous conservation genetics programs attempt to offset this
problem in XXX, and it has long been known that in artificial selection
breeding programs that selection can decrease effective population size
\parencite{Robertson1966-fs}. Furthermore, the role of evolution in determining
the levels of deleterious mutations in humans has been the subject of much
study.

processes approximately act to alter the variance in allele frequency change
between generations.

When
drift acts alone, deleterious alleles are only guaranteed to be removed by
selection when they're

a population can only remove mutations stronger than the
inverse of the population size ($N_e |s| > 1$).

@@

-

@@

Depending on the number of features, this can be incredibly memory intensive.
